Repeatability of Pre-Flashover Fire Patterns on Gypsum Wallboard

### 2015-04-10 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
update thesis with burn images

\begin{figure}[p]
	\centering
	\includegraphics[trim=1.0in, 0.2in, 1.0in, 0.0in, clip=true]{../Figures/IWGB_NG_0_15m}
	\includegraphics[trim=1.0in, 0.2in, 1.0in, 0.0in, clip=true]{../Figures/IWGB_NG_0m} \\	
	\caption[Photographs of the fire effects on the instrumented gypsum wallboard exposed to the natural gas burner fires]{Photographs of the fire effects on the instrumented gypsum wallboard exposed to the natural gas burner fires. For the image on the left, the burner was positioned 0.15~m from the wall.  For the image on the right, the burner was positioned 0.0~m from the wall.}
	\label{IWGB_NG_patterns}
\end{figure}

>>>>

\begin{figure}[p]
	\centering
	\includegraphics[trim=19.0in 5.0in 19.0in 15.0in, clip=true, width=0.4\columnwidth]{../Figures/IWGB_NG_0_15m}
	\includegraphics[trim=19.0in 5.0in 19.0in 15.0in, clip=true, width=0.4\columnwidth]{../Figures/IWGB_NG_0m} \\	
	\caption[Photographs of the fire effects on the instrumented gypsum wallboard exposed to the natural gas burner fires]{Photographs of the fire effects on the instrumented gypsum wallboard exposed to the natural gas burner fires. For the image on the left, the burner was positioned 0.15~m from the wall.  For the image on the right, the burner was positioned 0.0~m from the wall.}
	\label{IWGB_NG_patterns}
\end{figure}

\begin{figure}[p]
	\centering
	\includegraphics[trim=18.0in 4.0in 21.0in 14.0in, clip=true, width=0.4\columnwidth]{../Figures/IWGB_Gas_0_15_pattern}
	\includegraphics[trim=18.0in 2.6in 18.0in 11.7in, clip=true, width=0.4\columnwidth]{../Figures/IWGB_Gas7_0_8m} \\	
	\caption[Photographs of the fire effects on the instrumented gypsum wallboard exposed to the gasoline burner fires]{Photographs of the fire effects on the instrumented gypsum wallboard exposed to the gasoline burner fires. For the image on the left, the burner was positioned 0.15~m from the wall.  For the image on the right, the burner was positioned 0.8~m from the wall.}
	\label{IWGB_Gas_patterns}
\end{figure}

\begin{figure}[p]
	\centering
	\includegraphics[trim=10.3in 9.0in 10.3in 20.0in, clip=true, width=0.4\columnwidth]{../Figures/IWGB_Gas5_0m_prebrush}
	\includegraphics[trim=7.0in 3.5in 8.0in 18.5in, clip=true, width=0.4\columnwidth]{../Figures/IWGB_Gas5_0m_postbrush} \\		
	\caption[Photographs of the effect of soot removal on the instrumented gypsum wallboard exposed to the gasoline burner fires]{Photographs of the fire effects on the instrumented gypsum wallboard exposed to the gasoline burner fires. For the image on the left, the burner was positioned 0.0~m from the wall.  For the image on the right, the same panel after the soot was blown off, clean burn area is evident.}
	\label{IWGB_Gas_0m_patterns}
\end{figure}

\begin{figure}[p]
	\centering
	\includegraphics[trim=0.0in 0.0in 0.0in 0.0in, clip=true, width=0.4\columnwidth]{../Figures/IWGB_PUF5_0_15m}
	\includegraphics[trim=20.0in 1.0in 20.0in 16.4in, clip=true, width=0.4\columnwidth]{../Figures/IWGB_PUF12_0_8m} \\	
	\caption[Photographs of the fire effects on the instrumented gypsum wallboard exposed to the polyurethane foam fires]{Photographs of the fire effects on the instrumented gypsum wallboard exposed to the polyurethane foam fires. For the image on the left, the burner was positioned 0.15~m from the wall.  For the image on the right, the burner was positioned 0.08~m from the wall.}
	\label{IWGB_PUF_patterns}
\end{figure}

\begin{figure}[p]
	\centering
	\includegraphics[trim=5.0in 1.7in 5.0in 15.0in, clip=true, width=0.4\columnwidth]{../Figures/IWGB_PUF8_0m_pattern2}
	\includegraphics[trim=5.0in 3.5in 5.0in 13.0in, clip=true, width=0.4\columnwidth]{../Figures/IWGB_PUF9_0m_pattern} \\	
	\caption[Photographs of the fire effects on the instrumented gypsum wallboard exposed to replicate polyurethane foam fires]{Photographs of the fire effects on the instrumented gypsum wallboard exposed to replicate polyurethane foam fires with the burner positioned 0.0~m from the wall.}
	\label{IWGB_PUF_0m_patterns}
\end{figure}
